Sentence Generation as Planning with Probabilistic LTAG\\

### 2010-05-19 trunk/Papers/pcrisp-10/crisp.tex
Typos.

\section{Sentence Generation as Planning}
\label{sec:crisp}
In this section we review the original non-statistical {\sc crisp} system \cite{kollerstone2007}. 
Following {\sc spud} \cite{stonedoran1997}, {\sc crisp} is based on a declarative description of the sentence generation problem using {\sc tag}. Given a knowledge base, a communicative goal and a grammar, we require to find a grammatical {\sc tag} derivation that is consistent with this knowledge base and satisfies a communicative goal. A number of semantic and pragmatic constraints that must be satisfied by the solution can be added, for instance to enforce generation of unambiguous refering expressions. \newcite{kollerstone2007} describe how to encode this problem into an AI planning problem, that can be solved efficiently by off-the-shelf planners. We describe the general mechanism in the following section and then review the encoding into planning in section \ref{ssec:crispdomain}. 
\begin{figure*}[th]
\begin{center}
\includegraphics[width=.8\textwidth]{figures/grammar.pdf}
\caption{\label{fig:grammar}(a) An example grammar with semantic content. (b) A derivation for ``the cat eats raw tuna''. }
\end{center}
\end{figure*}

@@

In a derivation we may only include elementary trees whose semantic content has an instantiation in the knowledge base. For each substitution and adjunction, the semantic role associated with the role of the target node is unified with the `self' role of the child tree. For example, given the knowledge base 
{\it \{cat($i_2$), tuna($i_3$), raw($i_3$), eats($i_1$,$i_2$,$i_3$)\}} and the grammar in \ref{fig:grammar}(a), {\sc crisp} could produce the derivation in \ref{fig:grammar}(b).

@@

Figure \ref{fig:crisp-operators} shows planning operators for part of the grammar in figure \ref{fig:grammar}(a).
The preconditions of the operators require that a suitable open substitution node (i.e. of the correct category) or internal node for adjunction exists in the partial derivation. In the operator effect, open substitution nodes are closed and new identifiers are created for each substitution node and internal node in the new tree. Given the knowlede base from above, a plan corresponding to the derivation in figure \ref{fig:grammar} would be $\langle${\it S-eats-1(root, i1, i2, i3), NP-cat-2(subj-1, i2), NP-tuna-3(obj-1, i3), N-raw-4(obj-1, i3)}$\rangle$

>>>>

\section{Sentence Generation as Planning}
\label{sec:crisp}
In this section we review the original non-statistical {\sc crisp} system \cite{kollerstone2007}. 
Following {\sc spud} \cite{stonedoran1997}, {\sc crisp} is based on a declarative description of the sentence generation problem using {\sc tag}. Given a knowledge base, a communicative goal and a grammar, we require to find a grammatical {\sc tag} derivation that is consistent with this knowledge base and satisfies a communicative goal. A number of semantic and pragmatic constraints that must be satisfied by the solution can be added, for instance to enforce generation of unambiguous refering expressions. \newcite{kollerstone2007} describe how to encode this problem into an AI planning problem, that can be solved efficiently by off-the-shelf planners. We describe the general mechanism in the following section and then review the encoding into planning in section \ref{ssec:crispdomain}. 
\begin{figure*}[th]
\begin{center}
\includegraphics[width=.8\textwidth]{figures/grammar.pdf}
\caption{\label{fig:grammar}(a) An example grammar with semantic content. (b) A derivation for ``the cat eats the raw fish''. }
\end{center}
\end{figure*}

@@

In a derivation we may only include elementary trees whose semantic content has an instantiation in the knowledge base. For each substitution and adjunction, the semantic role associated with the role of the target node is unified with the `self' role of the child tree. For example, given the knowledge base 
{\it \{cat($i_2$), fish($i_3$), raw($i_3$), eats($i_1$,$i_2$,$i_3$)\}} and the grammar in \ref{fig:grammar}(a), {\sc crisp} could produce the derivation in \ref{fig:grammar}(b).

@@

Figure \ref{fig:crisp-operators} shows planning operators for part of the grammar in figure \ref{fig:grammar}(a).
The preconditions of the operators require that a suitable open substitution node (i.e. of the correct category) or internal node for adjunction exists in the partial derivation. In the operator effect, open substitution nodes are closed and new identifiers are created for each substitution node and internal node in the new tree. Given the knowlede base from above, a plan corresponding to the derivation in figure \ref{fig:grammar} would be $\langle${\it S-eats-1(root, i1, i2, i3), NP-cat-2(subj-1, i2), NP-fish-3(obj-1, i3), N-raw-4(obj-1, i3)}$\rangle$
